Modeling the Circumnuclear Mediums and Accetion Rates of Quiescent Supermassive Black Holes

### 2014-12-14 ms.tex
Updating figures to reflect the new parameterized approach.

\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\ff}{\rm ff}
\newcommand{\tff}{t_{\ff}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\EIa}{E_{\rm Ia}}
\newcommand{\RateIa}{R_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}

@@

\newcommand{\pyear}{{\rm yr}^{-1}}
\newcommand{\tage}{t_{\star}}
\renewcommand{\th}{t_h}

@@

This paper is organized as followed.  In $\S\ref{sec:model}$ we
describe our model, including the sample of galaxies used in our
analysis ($\S\ref{sec:sample}$) and our numerical procedure for
calculating the steady-state hydrodynamic profile of the CNM
($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
results.  In $\S\ref{sec:applications}$ we describe applicaiton of our
results, including a comparison of our gas profiles to those inferred
from {\it Chandra} observations and to the measured $L_X-\Mbh$
relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
$\S\ref{sec:summary}$ we summarize our results.
\section{Model}
\label{sec:model}

\subsection{Galaxy Sample}

\label{sec:sample}
%AG:It is unclear whether if/how the Nuker profile will show up in
%this parametrized study.
{\bf BDM: we may show plot of NUKER masses, $\Gamma$'s, etc here to (1) motivate the parametric study; (2) in individual cases we may want to compare solutions to specific galaxies.}

Our sample includes 61 early-type galaxies from
\citetalias{WangMerritt:2004a}, as represent a subset of a larger
sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
focus on elliptical galaxies because we are interested in isolating
SMBHs fed by the steady mass loss from the relatively old stellar
population, instead of fresh gas flowing into the sphere of influence
from larger scales.

The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
\begin{equation}
  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
\end{equation}
The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.

Given $I(\xi)$ we follow the procedure outlined by
\citetalias{WangMerritt:2004a} to compute the spherically-symmetric
stellar density profile $\rhostar(r)$ and stellar mass profile
$M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
our model.  For reference, note that stellar density $\rhostar\sim
r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
\gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
$\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
%%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
%%calculated from an outdated M-sigma. It would be bizarre to use 2
%%different relations.

@@

When possible our results are expressed in terms of the wind heating
parameter $\vw$; the power-law slope of the density profile
$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vw0^2+\sigma^2$,
where the $\sigma$ accounts for shock heating between stellar winds moving
with respect to each other with relative velocity $\sigma$, and $\vwO$
is a free parameter accounting for additional sources of
heating.  $\vw$ may be calculated analytically (for a given $\Mbh$ and
$\vwO$) using $\vw=\chi \vwO$, where

@@

First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by.
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
\times 10^6\,\chi v_{500}^2 \,\,{\rm K} 
\label{eq:Tanalytic}
\end{align}
%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}

Demanding hydrostatic equilibrium at the stagnation point provides an expression for the stagnation radius
\begin{align}
  \x=\frac{1}{2 \zeta^2 n}\left[ \frac{\Mstar}{\Mbh}\left(A-n\right)+\left(B-n\right)\right],
  \label{eq:stag_analytic}
\end{align}

@@

The importance of conductive heating can be estimated by comparing its
magnitude to that of wind heating, viz.~
\begin{align} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim
10.5 \left(\frac{\eta}{0.1}\right)^{-1}\left(\frac{r_{\rm s}}{r_{\rm
soi}}\right)^{-\beta} v_{500}^{9}\chi^{9} \nonumber \\ &\sim
4.53 \, 0.43^{\beta-1} \left(\frac{\eta}{0.1}\right)^{-1}
M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}\chi^{9-2\beta}
\label{eq:condRatio1}
\end{align}

where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in
the second equality have made use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm
  s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm
  soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that
conductive heating is important near the stagnation radius for high
values of $v_{\rm w} \gtrsim 500$ km s$^{-1}$ and $\eta \gtrsim 0.1$,
but that it is safely neglected to first order for lower heating
rates. {\bf AG:Should probably include mass. Although this is tricky
  as cusp and core galaxies have opposite dependencies on mass.}

@@

\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}

@@

\begin{eqnarray}
\eddr&\approx&
  \begin{cases}
    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
    \chi^{-3.8} v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
    2.4 \times 10^{-5} \Mbheight^{0.48} 
    \chi^{-2.4} v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}

The stellar density at the stagnation radius (eq.~[\ref{eq:stag_simple}]) is usefully approximated as
\begin{eqnarray}
  && \rho_{\star}(r_{\rm s}) \approx \nonumber \\
  && \begin{cases}
    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\chi^{2.2}\,{\rm g\,cm^{-3}}
    & \text{core} \\
    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}\chi^{3.6}
    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
  \end{cases}
  \label{eq:rhostarrs}
\end{eqnarray}

The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be roughly estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}(\rs)},
  \label{eq:mdot_gas}
\end{align}
from which one derives 
\begin{align}
  \rho(\rs)\simeq
  \begin{cases}
    5 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
    \, {\rm g \, cm^{-3}}& \text{core}\\
    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}
  \end{cases}
  \label{eq:rhors}
\end{align}

@@

Rewriting equation (\ref{eq:mdot_gas}) as
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{t_{\ff}} =\frac{4 \pi}{3} \rs^2 \rho(\rs) v_{\ff}(\rs)
\end{align}
we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
\begin{align}
  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}},
  \label{eq:rs_simple}
\end{align}
where in the second line we have used the fact that $v_{w}^{2}/2 =
c_s^2/(\gamma-1)$ at $\rs$.  Thus, provided that a stagnation radius
exists which is interior to the sphere of influence radius, the
accretion rate predicted by our model is quite close to $\dot{M}_{\rm
  B}$.
 %({\bf BDM: Check - as this depends on
 % whether eq 10 is correct})

@@

Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 200, 500, 1000 km s$^{-1}$.

Figure~\ref{fig:profiles} shows three representative profiles of the density $\rho(r)$, temperature $T(r)$, and radial velocity $|v(r)|$.  As expected, the gas density increases towards the SMBH.  For some profiles (e.g. NGC1172 and NGC4478) the density $\rho$ follows a power law from the stagnation radius (squares in Fig.~\ref{fig:profiles}) inwards $\rho \propto r^{-n}$ with $n \approx 1$. Note that this is shallower than the $-3/2$ power law for Bondi accretion. However, the power law behavior does not extend through all radii, and the gas density profile may have breaks mirroring those in the stellar density profile. For example, NGC4365 has a prominent break in the gas density profile, near the stagnation radius. This coincides with the location
of the break in the stellar light profile ($\rb$). The temperature profile is relatively flat at large radii, but increases as $\propto
1/r^{k}$ interior to the sphere of influence, where $k$ is smaller than 1--the power expected for virialized gas.  The inwardly
directed velocity increases towards the hole approaching the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$ interior to the sonic point, and then increases outwards towards large radii.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...
% AG -- I am somewhat concerned about boundary effects in
% NGC3115. Perhaps the break in the gas density profile is due to
% boundary effects--I know that in this case the break is not
% associated with a break in the stellar density profile

Figure~\ref{fig:stag} (top panel) shows numerical results for the stagnation radius $r_{\rm s}$ where the radial velocity goes to zero (expressed in ratio to the radius of the SMBH sphere of influence $r_{\rm soi}$), with different colors representing different values of $v_{w,0}$.  Cusp and core galaxies are marked with square and triangles, respectively.  
%The solid line is a power law fit through the cusp galaxies, while the dotted line is a power law fit through the core galaxies.  {\bf BDM: I see no lines!}

Our results for $r_{\rm s}/r_{\rm soi}$ can be compared directly to our analytic estimate in equation \ref{eq:stag_analytic}.  The bottom panel of Figure \ref{fig:stag} shows the fractional difference between our numerical and analytic results for $r_{\rm s}/r_{\rm soi}$.  The generally good agreement (especially for $v_{w,0}$ = 500, 1000 km s$^{-1}$) provides a useful check of the numerical results.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), velocity  ({\it bottom}), and
    interior X-ray luminosity ({\it bottom}), calculated for three
    characteristic galaxies from our samples: NGC1172 ({\it blue}),
    NGC4478 ({\it green}), and NGC3115 ({\it black}).  Different line
    styles denote different values of the effective wind heating rate,
    $v_{w,0}$=500 km s$^{-1}$ ({\it solid}) and 200 km s$^{-1}$ ({\it
     dot-dashed}).}
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w,0}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols represent $v_{w,0} =$ 200, 500, and 1000 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies, while
    triangles correspond to cores. \emph{Bottom panel}: Fractional
    difference between our numerical calculation of $r_{\rm s}/r_{\rm
      soi}$ and the analytic result in
    equation~(\ref{eq:stag_analytic}). }
\end{figure}

@@

\subsubsection{Stellar winds} Although most of the mass supplied to the CNM by stellar winds occurs during the giant AGB phase, these winds represent a negligible heating source compared to the random wind velocity because the wind velocity $\lesssim 40$ km s$^{-1}$ is much less than the stellar potential $\sigma$.

@@

  \begin{align}
    v_{\rm w,0}^{\rm p} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
&\approx&  40\epsilon^{1/2}\left(\frac{\bar{L}_{\rm sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2} \left(\frac{\eta}{0.1}\right)^{-1/2}\,{\rm km\,s^{-1}},
  \end{align}

>>>>

\newcommand{\phirs}{\frac{G \Menc}{\rs}}
\newcommand{\soi}{\rm soi}
\newcommand{\rsoi}{r_{\soi}}
\newcommand{\rIa}{r_{\rm Ia}}
\newcommand{\EIa}{E_{\rm Ia}}
\newcommand{\RateIa}{R_{\rm Ia}}
\newcommand{\sigsoi}{\sigma_{\soi}}

@@

\newcommand{\pyear}{{\rm yr}^{-1}}
\newcommand{\tage}{t_{\star}}
\renewcommand{\th}{t_h}
\newcommand{\tcool}{t_{\rm cool}}
\newcommand{\tff}{t_{\rm ff}}

@@

This paper is organized as followed.  In $\S\ref{sec:model}$ we
describe our model, including the sample of galaxies used in our
analysis ($\S\ref{sec:sample}$) and our numerical procedure for
calculating the steady-state hydrodynamic profile of the CNM
($\S\ref{sec:hydro}$).  In $\S\ref{sec:results}$ we describe our
results.  In $\S\ref{sec:applications}$ we describe applicaiton of our
results, including a comparison of our gas profiles to those inferred
from {\it Chandra} observations and to the measured $L_X-\Mbh$
relationship.  In $\S\ref{sec:discussion}$ we discuss our results.  In
$\S\ref{sec:summary}$ we summarize our results.
\section{Model}
\label{sec:model}
\subsection{Galaxy models}
\citealt{LauerFaber+:2007a} used Hubble WFPC2 imaging to measure the
surface brightness profiles for hundred of nearby early type
galaxies. The measured surface brightness profile can generally be
well fit using a Nuker law

\begin{equation}
  I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
\end{equation}
The Nuker profile is a broken power law which transitions from an
inner power law slope, $\Gamma$, to an outer power law slope, $\beta$,
at a break radius, $\rb$.

Assuming spherical symmetry this corresponds to a stellar density
$\rhostar \sim r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim
r^{-1-\beta}$ for $r \gg \rb$. Thus, we adopt a broken power law for 
$\rhostar$

\begin{align}
\rho_\star = 
\begin{cases}
\rho_\star(\rsoi) \left(r/\rsoi\right)^{-1-\Gamma} & r \leq r_b\\
\rho_\star(r_b) \left(r/r_b\right)^{-1-\beta} & r > r_b,
\end{cases}
\end{align}

where $\rho_\star(\rsoi)$ is the stellar density at the black hole
sphere of influence, $\rsoi$. $\rho_\star(\rsoi)$ is chosen so that
the stellar mass inside $\rsoi$, $\Mstar(\rsoi)$, is equal to the
black hole mass.  $\rsoi=G \Mbh/\sigma^2$. Using the $\Mbh-\sigma$ relation
from \citealt{Gultekin+09}

 \begin{align}
M_{\bullet} \simeq 2\times 10^{8}\left(\frac{\sigma}{200\,{\rm
      km\,s^{-1}}}\right)^{5.1}M_{\odot}, 
\label{eq:Msigma}
\end{align}

we obtain $\rsoi \approx 14 M_{\bullet,8}^{0.6}$. In order to
completely specify the galaxy model we must choose $\Mbh$, $\Gamma$, $r_b$,
and $\beta$. We compute models for three different models of
$\Mbh$: $10^6$, $10^7$, $10^8 \Msun$. In the
\citealt{LauerFaber+:2007a} sample the distribution of the $\Gamma$s
is bimodal, with a concentration of core galaxies with $\Gamma \lsim
0.3$ and a concentration of cusp galaxies with $\Gamma \gsim
0.7$. We calculate models for $\Gamma=0.8$ and $\Gamma=0.1$.

We are interested in the gas flow on scales smaller than
the break radius $\rb$, which typically occurs at a radius of 100s of
parsecs. Thus, we fix $\beta$ to be 2 {\bf AG:I have not yet checked this
  directly via numerical experiments}.  The presence of $\rb$ is 
necessary for to obtain a converged steady state for some regions of
our parameter space. For cusp galaxies, $r_b$ is a few hundred parsecs
independently of $\Mbh$. We adopt $\rb=100$ pc for our cusp
galaxies ($\Gamma=0.8$), while for our core galaxy models we use the
scaling relation...{\bf AG: Need to figure out normalization for
  scaling relation from Lauer. Fixed rb at a given Mbh only has a
  factor of a few effect on rs--this will be discussed in the section
  on numerical solutions.}

% \subsection{Galaxy Sample}

% \label{sec:sample}
% %AG:It is unclear whether if/how the Nuker profile will show up in
% %this parametrized study.
% {\bf BDM: we may show plot of NUKER masses, $\Gamma$'s, etc here to (1) motivate the parametric study; (2) in individual cases we may want to compare solutions to specific galaxies.}

% Our sample includes 61 early-type galaxies from
% \citetalias{WangMerritt:2004a}, as represent a subset of a larger
% sample of \citet{FaberTremaine+:1997a} with Hubble WFPC2 imaging.  We
% focus on elliptical galaxies because we are interested in isolating
% SMBHs fed by the steady mass loss from the relatively old stellar
% population, instead of fresh gas flowing into the sphere of influence
% from larger scales.

% The surface brightness of each galaxy in the sample is parameterized by a Nuker Law (WM04; their Table 1),
% \begin{equation}
%   I(\xi)=I_b 2^{(\beta-\Gamma)/\alpha} \xi^{-\Gamma} (1+\xi^\alpha)^{-(\beta-\Gamma)/\alpha}, \,\,\,\xi\equiv\frac{r}{r_b}.
% \end{equation}
% The Nuker profile is a broken power law which transitions from an inner power law slope, $\Gamma$, to an outer power law slope, $\beta$, at a break radius, $\rb$.

% Given $I(\xi)$ we follow the procedure outlined by
% \citetalias{WangMerritt:2004a} to compute the spherically-symmetric
% stellar density profile $\rhostar(r)$ and stellar mass profile
% $M_{\star}(r) = 4\pi \int \rhostar r^{2}dr$, both of which are used in
% our model.  For reference, note that stellar density $\rhostar\sim
% r^{-1-\Gamma}$ for $r \ll \rb$ and $\rhostar\sim r^{-1-\beta}$ for $r
% \gg \rb$.  Since $\Gamma\approx 1$ for ``cusp" galaxies, while
% $\Gamma\approx 0$ for ``core" galaxies, at small radii $\ll \rb$ we
% thus have $\rhostar \propto r^{-\alpha}$ and $M_{\star} \propto
% r^{\beta}$ with $\beta = 3-\alpha \approx 1-2$.  For each galaxy the
% SMBH mass $\Mbh$ is determined from the $\Mbh-\sigma$ relationship.
% %%AG-ugh I just took the Mbh from Wang & Merritt, which I guess is
% %%calculated from an outdated M-sigma. It would be bizarre to use 2
% %%different relations.

@@

When possible our results are expressed in terms of the wind heating
parameter $\vw$; the power-law slope of the density profile
$n$ (also evaluated at $r = \rs$); Note that $\vw^2=\vwO^2+\sigma^2$,
where the $\sigma$ accounts for shock heating between stellar winds moving
with respect to each other with relative velocity $\sigma$, and $\vwO$
is a free parameter accounting for additional sources of
heating.  $\vw$ may be calculated analytically (for a given $\Mbh$ and
$\vwO$) using $\vw=\chi \vwO$, where

@@

First, by demanding continuity of the entropy derivative at the stagnation radius, the temperature at the stagnation radius is given by.
\begin{align}
T \simeq \frac{\gamma-1}{\gamma}\frac{\mu m_p v_{w}^{2}}{2} \approx 3.7
\times 10^6\ \, v_{500}^2 \,\,{\rm K} 
\label{eq:Tanalytic}
\end{align}
%{\bf BDM: i picked $\mu = 0.62$ and stick to it.}

Demanding hydrostatic equilibrium at the stagnation point provides an
expression for the stagnation radius

\begin{align}
  \frac{\rs}{\rsoi}=\frac{1}{2 \zeta^2 n}\left[
   \frac{\Mstar(\rs)}{\Mbh}\left(\frac{9-\Gamma}{2}-n\right)+\left(\frac{7}{2}-n\right)\right]
 \label{eq:stag_analytic}
\end{align}

@@

The importance of conductive heating can be estimated by comparing its
magnitude to that of wind heating, viz.~
\begin{align} \left.\frac{\nabla\cdot(\kappa \nabla T)}{q v_{\rm
w}^{2}/2}\right|_{r_{\rm s}} &\sim \frac{2t_{\rm h}\kappa_0
T^{7/2}}{r_{\rm s}^{2}\eta \rho_{\star}(r_{\rm s}) v_{\rm w}^{2}}
\nonumber \\ &\sim
53 \eta_{0.02}^{-1}\left(\frac{r_{\rm s}}{r_{\rm
soi}}\right)^{-\beta} v_{500}^{9} \nonumber \\ &\sim
23 \,\, 0.43^{\beta-1} \eta_{0.02}^{-1}
M_{\bullet,8}^{-1.2+0.4\beta} v_{500}^{9-2\beta}
\label{eq:condRatio1}
\end{align}

where we have approximated $\nabla^{2} \sim 1/r_{\rm st}^{2}$ and in
the second equality have made use of equations (\ref{eq:Tanalytic}),
(\ref{eq:stag_simple}) and have approximated $4\pi r_{\rm
  s}^{3}\rho_{\star}(r_{\rm s}) \approx M_{\bullet}(r_{\rm s}/r_{\rm
  soi})^{\beta}$ with $\beta \approx 1-2$.  We thus see that
conductive heating is important near the stagnation radius for high
values of $v_{\rm w} \gtrsim 300$ km s$^{-1}$ and $\eta=0.02$, but
that it is safely neglected to first order for lower heating
rates. {\bf AG:Note that threshold vw is rather--the 300 km/s is
  estimated for cusp galaxies. The change in normalization is due to
  the change in the fiducial eta from 0.1 to 0.02. This seems like bad
  news. Should probably include mass. Although this is tricky as cusp
  and core galaxies have opposite dependencies on mass. Perhaps we
  will have to lean on the saturated argument more if we really would
  like to avoid conductivity. Or perhaps including conductivity is
  truly unavoidable. ):}

@@

\begin{eqnarray}
  \dot{M} &=& \frac{\eta \Menc(\rs)}{\th} \nonumber \\
&\approx&
  \begin{cases}
    2.9 \times 10^{-5} M_{\bullet,8}^{1.76}
    v_{500}^{-3.8}  \eta_{0.02} \Msun \, \pyear& \text{core} \\
    5.3 \times 10^{-5} M_{\bullet,8}^{1.48} 
    v_{500}^{-2.4}  \eta_{0.02} \Msun \, \pyear  & \text{cusp}, 
  \end{cases}
  \label{eq:mdot_analytic}
\end{eqnarray}

@@

\begin{eqnarray}
\eddr&\approx&
  \begin{cases}
    1.3 \times 10^{-5} M_{\bullet,8}^{0.76}
    v_{500}^{-3.8}  \eta_{0.02}   & \text{core} \\
    2.4 \times 10^{-5} \Mbheight^{0.48} 
    v_{500}^{-2.4}  \eta_{0.02}   & \text{cusp}, 
  \end{cases}
  \label{eq:eddr_analytic}
\end{eqnarray}

The stellar density at the stagnation radius (eq.~[\ref{eq:stag_simple}]) is usefully approximated as
\begin{eqnarray}
  && \rho_{\star}(r_{\rm s}) \approx \nonumber \\
  && \begin{cases}
    9.4 \times 10^{-19}M_{\bullet,8}^{-1.2}v_{500}^{2.2}\,{\rm g\,cm^{-3}}
    & \text{core} \\
    1.1 \times 10^{-18} M_{\bullet,8}^{-1.5}v_{500}^{3.6}
    \,{\rm g\,cm^{-3}}  & \text{cusp}, 
  \end{cases}
  \label{eq:rhostarrs}
\end{eqnarray}

The density of gas at the stagnation radius $\rho(r_{\rm s})$ can be roughly estimated by using equations (\ref{eq:stag_simple}) and (\ref{eq:mdot_analytic}) in conjunction with an alternative estimate of the mass accretion rate as the gaseous mass within the stagnation radius divided by the free-fall time $t_{\rm ff}(\rs) = (r_{\rm s}^{3}/GM_{\bullet})^{1/2}$, viz.
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff(\rs)},
  \label{eq:mdot_gas}
\end{align}
from which one derives 
\begin{align}
  \rho(\rs)\simeq
  \begin{cases}
    5 \times 10^{-26} \Mbheight^{-0.2} v_{500}^{-0.8}  \eta_{0.02} \,
    \, {\rm g \, cm^{-3}}& \text{core}\\
    9 \times 10^{-26}  \Mbheight^{-0.5} v_{500}^{0.6}  \eta_{0.02} \,\, {\rm g \,cm^{-3}} & \text{cusp}
  \end{cases}
  \label{eq:rhors}
\end{align}

Note that combining equations~\eqref{eq:mdot_analytic}
and~\eqref{eq:mdot_gas} we can rewrite the $\rho(\rs)$

\begin{align}
\rho(\rs)=\frac{3 q(\rs) \tff(\rs)}{2-\Gamma}.
\label{eq:rhors2}
\end{align}

@@

Rewriting equation (\ref{eq:mdot_gas}) as
\begin{align}
  &\dot{M}\simeq\frac{(4 \pi/3) \rs^3 \rho(\rs)}{\tff} =\frac{4
    \pi}{3} \rs^2 \rho(\rs) v_{\rm ff}(\rs)
\end{align}
we note the qualitative similarity between this expression and the Bondi formula (equation~[\ref{eq:bondi}]) with the exception that $\rb$ is replaced by $\rs$.  Using equation (\ref{eq:stag_simple})
\begin{align}
  \rs\approx\frac{7}{2}\frac{G \Mbh}{\vwO^2} \approx \frac{14}{3}\frac{GM_{\bullet}}{c_{s}^{2}},
  \label{eq:rs_simple}
\end{align}
where in the second line we have used the fact that $v_{w}^{2}/2 =
c_s^2/(\gamma-1)$ at $\rs$.  Thus, provided that a stagnation radius
exists which is interior to the sphere of influence radius, the
accretion rate predicted by our model is quite close to $\dot{M}_{\rm
  B}$.
 %({\bf BDM: Check - as this depends on
 % whether eq 10 is correct})

@@

Numerical solutions are calculated for each galaxy for three different values of the stellar wind heating parameter $v_{w,0}$ = 300, 600, 1200 km s$^{-1}$.

Figure~\ref{fig:profiles} shows profiles of the density $\rho(r)$,
temperature $T(r)$, and radial velocity $|v(r)|$, for the cusp
($\Gamma=0.8$) solutions within our grid.  As expected, the gas
density increases towards the SMBH $\rho\propto r^{-n}$ with
$n\simeq1$.  Note that this is shallower than the $-3/2$ power law for
Bondi accretion. However, the power law behavior does not extend
through all radii, and the gas density profile has a break coincident
with the location of the break in the stellar light profile ($\rb=100$
pc). The temperature profile is relatively flat at large radii, but
increases as $\propto 1/r^{k}$ interior to the sphere of influence,
where $k$ is smaller than 1--the power expected for virialized gas.
The inwardly directed velocity increases towards the hole approaching
the expected free-fall rate $v \propto v_{\rm ff}\propto r^{-1/2}$
interior to the sonic point, and then increases outwards towards large
radii.
% {\bf BDM: I made this up - in general we need
%   more explanation of what the plots are actually showing, with some
%   physical explanation.}
% AG -- things are not quite approaching Bondi on the inner grid. I
% don't have a good physical explanation yet...

Figure~\ref{fig:stag} (top panel) shows numerical results for the
stagnation radius $r_{\rm s}$ where the radial velocity goes to zero
(expressed in ratio to the radius of the SMBH sphere of influence
$r_{\rm soi}$), with different colors representing different values of
$v_{w,0}$.  Cusp and core galaxies are marked with square and
triangles, respectively.

We also show the simplified analytic result corresponding to $\rs$
approximated from \eqref{eq:stag_simple} as a solid black line. For
$\vwO$, we find good agreement with the analytic prediction. However,
\eqref{eq:stag_simple} is only valid that $\Mstar(\rs) \ll \Mbh$, and
this approximation breaks down for small $\vwO$. In fact, $\rs$
diverges for smaller $\vwO$.

{\bf AG perhaps it would be better to solve the implicit equation for
  rs/rsoi, and plot this in the top panel--assuming a fixed n of say
  1}. We may also compare our numerical results $r_{\rm s}/r_{\rm
  soi}$ an be compared directly to our analytic estimate in equation
\ref{eq:stag_analytic}.  The bottom panel of Figure \ref{fig:stag}
shows the fractional difference between our numerical and analytic
results for $r_{\rm s}/r_{\rm soi}$.  The good agreement provides a
useful check of the numerical results.

@@

\begin{figure}
  \includegraphics[width=\columnwidth]{profiles.eps}
  \caption{\label{fig:profiles}Radial profiles of the CNM density
    ({\it top}), temperature ({\it middle}), velocity ({\it bottom}),
    and interior X-ray luminosity ({\it bottom}) calculated for the
    cusp galaxies ($\Gamma=0.8$) within our grid.  Different colors
    denote different values of the effective wind heating rate,
    $\vwO=1200$ km s$^{-1}$ ({\it blue}), $\vwO$=600 km s$^{-1}$ ({\it
      orange}), and 300 km s$^{-1}$ ({\it green}).  Different
    linestyles correspond to different values of $\Mbh$, $\Mbh=10^6
    \Msun$ ({\it dot-dashed}), $\Mbh=10^7 \Msun$ ({\it solid}), and
    $\Mbh=10^8 \Msun$ ({\it dashed}). Squares mark out the location of
    the stagnation radius for each solution.
 }
\end{figure}

\begin{figure}
  \includegraphics[width=\columnwidth]{rs.eps}
  \caption{\label{fig:stag} \emph{Top panel:} Stagnation radius
    $r_{s}$ (in units of the radius of the sphere of influence $r_{\rm
      soi} = GM_{\bullet}/\sigma^{2}$) for galaxies in our sample as a
    function of the ratio of the effective wind heating rate $v_{w,0}$
    to the stellar velocity dispersion $\sigma$.  Green, orange, and
    blue symbols represent $v_{w,0} =$ 300, 600, and 1200 km s$^{-1}$,
    respectively.  Squares correspond to cusp galaxies, while
    triangles correspond to cores. \emph{Bottom panel}: Fractional
    difference between our numerical calculation of $r_{\rm s}/r_{\rm
      soi}$ and the analytic result in
    equation~(\ref{eq:stag_analytic}). }
\end{figure}

@@

\subsubsection{Stellar winds} 
{\bf AG: This section may have to be substantially modified in light
  of our more careful analysis of stellar winds.}

Although most of the mass supplied to the CNM by stellar winds occurs
during the giant AGB phase, these winds represent a negligible heating
source compared to the random wind velocity because the wind velocity
$\lesssim 40$ km s$^{-1}$ is much less than the stellar potential
$\sigma$.

@@

\begin{align}
  v_{\rm w,0}^{\rm p} &=&\left({\frac{2\epsilon t_h n_{\rm msp} \bar{L}_{\rm sd}}{\eta}}\right)^{1/2} \nonumber \\
  &\approx& 90\epsilon^{1/2}\left(\frac{\bar{L}_{\rm
        sd}}{10^{34}\,{\rm erg\,s^{-1}}}\right)^{1/2}
  \eta_{0.02}^{-1/2}\,{\rm km\,s^{-1}},
  \end{align}

  where $\epsilon< 1$ is the thermalization efficiency of the wind.
  The $\sim 30,000$ estimated MSPs in the Milky Way of stellar mass
  $6\times 10^{10}M_{\odot}$ (\citealt{Lorimer13}) corresponds to
  $n_{\rm msp}\simeq3 \times 10^{-40} $ MSPs g$^{-1}$, a number we
  assume in the numerical estimate.  Using the ATNF radio pulsar
  catalog (\citealt{Manchester+05}), we estimate the average spin-down
  luminosity of millisecond pulsars in the field (excluding those in
  globular clusters) to be $\bar{L}_{\rm sd} \sim 10^{34}$ erg
  s$^{-1}$ {\bf For eta=0.02 we cannot really
    say that vw from msps is negligible}
